---
title: "Practical Machine Learning Project"
author: "Allan Reyes"
date: "02/01/2015"
output: html_document
---

```{r echo=FALSE}
# setwd('~/Dropbox/moocs/jhu-pml')
```

### Introduction

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit, it is now possible to collect a large amount of data about personal activity relatively inexpensively.  These type of devices are part of the quantified self movement--a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech enthusiasts.  One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.  Participants were asked to perform barbell lifts correctly and incorrectly in 5 different ways.  In this project, the goal was to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict the manner in which they did their exercise.

### Load Data
```{r}
testing <- read.csv("data/pml-testing.csv",na.strings=c("NA",""))
training <- read.csv("data/pml-training.csv",na.strings=c("NA",""))
```



### Predict

```{r}
#TODO
predictions = rep('A', 20)
```


### Export Predictions

```{r}
pml_write_files = function(x) {
  n = length(x)
  for(i in 1:n){
    filename = paste0('predictions/problem_id_', i, '.txt')
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(predictions)
```

